---
title: "R Notebook"
output: html_notebook
---

```{r}
library(hash)
```

Let's first create a method to sample elements from a list 

```{r}
sample_values <- function(value_list,p) {
  value_length <- length(value_list)
  if(length(p) == 0) {
      probs <- rep(c(1/value_length),value_length)
  }
  else {
    probs <- p
  }
  index <- sample(seq(1,value_length),size=1,replace=TRUE,prob=probs) 
  
  return (value_list[index])
}
```
Then create a function to create random records, by randomly sampling for each field
```{r}

possible_values <- hash()
possible_values[["age"]] <- c("0-5","6-12","13-18","18-45","45-60","60+")
possible_values[["sex"]] <- c("Male", "Female", "Other") 
possible_values[["marital"]] <- c("Single", "Married", "Divorced", "Seperated", "Widowed") 
possible_values[["relationship"]] <- c("Self", "Spouse","Child","Parent","Other")
possible_values[["education"]] <- c("None" ,"Elementary", "Secodary", "Post-Secondary")  
  
possible_probabilities <- hash()
possible_probabilities[["age"]] <- c()
possible_probabilities[["sex"]] <- c(0.45,0.45,0.1)
possible_probabilities[["marital"]] <- c() 
possible_probabilities[["relationship"]] <- c()
possible_probabilities[["education"]] <- c()

random_person <- function() {
  h <- hash() 
  for(i in keys(possible_values)) {
    h[[i]] = sample_values(possible_values[[i]],possible_probabilities[[i]])
  }
  
  return (h)
}
```

Now let's create multiple records, to create a survey

```{r}
generate_records <- function(n) {
  people_list <- c()
  for(i in 1:n) {
    people_list <- append(people_list,random_person())
  }
  return (people_list)
}

generate_records(10)
```
Now that we have a survey, let's define edits as a boolean statement, where edits determine what is not allowed
```{r}
edits <- c({function(x) x>20},{function(x) x<15})
passes_edits <- function(edit_list,o) {
 passes = TRUE
 for(edit in edit_list) {
     passes <- passes & !edit(o)
 }
 
 return (passes) 
}

passing_records <- function(edit_list, record_list) {
  new_records <- c()
  for(i in 1:length(record_list)) {
    if(passes_edits(edit_list,record_list[[i]])) {
      new_records <- append(record_list[[i]],new_records)
    }
  }
  return (new_records) 
}

passing_records(edits,1:20)


```
Let's create our actual edits for the survey
```{r}
e1 <- {function(record) ((record[["age"]] == "0-5" | record[["age"]] == "6-12") & (record[["marital"]] != "Single"))}
e2 <- {function(record) ((record[["age"]] == "60+") & (record[["relationship"]] == "Child"))}
e3 <- {function(record) ((record[["relationship"]] == "Spouse") & (record[["marital"]] == "Single"))}
e4 <- {function(record) ((record[["age"]] == "0-5") & (record[["education"]] == "Post-Secondary"))}
e5 <- {function(record) ((record[["age"]] == "0-5" | record[["age"]] == "6-12" | record[["age"]] == "13-18") & (record[["relationship"]] == "Spouse"))}
e6 <- {function(record) ((record[["marital"]] == "Widowed") & (record[["relationship"]] == "Spouse"))}
e7 <- {function(record) ((record[["age"]] == "0-5") & (record[["relationship"]] == "Self"))}
```
Using these edits + survey data, let's create a gold dataset, of perfect data points. 
We do this by creating 5K random data points and removing the bad ones, leading to 3K data points. 
Later, we'll perturb the dataset so some records are incorrect, which will serve as the noisy dataset. 
```{r}

edit_list <- c(e1,e2,e3,e4,e5,e6,e7)
records <- generate_records(5000)
good_records <- passing_records(edit_list,records)
length(good_records)
```

The perturb function changes some fields from records (independently)
```{r}
peturb_records <- function(old_records,values) {
  good_records <- old_records
  for(i in 1:length(good_records)) {
    new_record <- copy(good_records[[i]])
    for(k in keys(new_record)) {
      if(runif(1)<0.2) {
        possible_values <- values[[k]]
        value <- sample_values(possible_values,c())
        new_record[[k]] <- value
      }
    }
    good_records[[i]] = new_record
  }
  
  return (good_records)
}

modified_records <- peturb_records(good_records,possible_values)
length(passing_records(edit_list,modified_records))
```
Let's now write our gold dataset and our noisy dataset to CSV files. 
```{r}
write_to_csv <- function(data_list,file_name) {
  ids <- c()
  for(i in 1:length(data_list)) {
    ids <- append(i,ids)
  }
  
  
  df <- data.frame(ids)
  all_as_list <- hash()

  for(i in 1:length(data_list)) {
    for(key in keys(data_list[[i]])) {
      all_as_list[[key]] <- append(data_list[[i]][[key]],all_as_list[[key]])
    }
  }
  
  column_names <- c("ids")
  
  for(i in keys(all_as_list)) {
    df <- cbind(df,all_as_list[[i]])
    column_names <- append(i, column_names)
  }
  
  colnames(df) <- column_names
  
  write.csv(df,file_name)
}

write_to_csv(good_records,"good_records.csv")
write_to_csv(modified_records,"error_records.csv")

```
